Robust Digital Envelope Estimation Via Geometric Properties of an Arbitrary Real Signal

### 2020-09-02 Papers/02_Pulses_Envelope/PulsesEnvelope.tex
added robustness proof and images to the paper

\documentclass{article}
% \usepackage{svg}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage{amsfonts} % \mathbb
\usepackage[margin=0.5in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage[backend=biber, style=apa]{biblatex}
\usepackage{amsmath}
\DeclareMathOperator{\sign}{sign}
\bibliography{bibli}

\title{Robust Digital Envelope Estimation Via Geometric Properties of an Arbitrary Real Signal}
\author{
  Carlos Tarjano
  \and 
  Valdecy Pereira
  }

@@

The angle $ \theta $ between the average direction and each of the vectors can be obtained via the relation of the slope of the respective lines, as in the expression $ \theta = \arctan( (m - \overline{m}) / (1 + m * \overline{m}) ) $. The radii of the equivalent circles are thus given by $ r_l = x_l / \sin (\theta_l) $ with the curvature given by $\kappa_l =1/r_l=\sin (\theta_l) / x_l$.

@@

% Therefore, the definition of the curvature becomes $ \kappa(x) = \frac{2 a}{\big( (b + 2 a x)^2 + 1 \big)^\frac{3}{2}} $ with the average curvature between points $ x_0 $ and $ x_1 $ given by equation \ref{eq:1}.

% \begin{equation} \label{eq:1}
%   \overline{\kappa}(x) = 
%   \frac{
%       \left( \dfrac{2 a x_1 + b}{\sqrt{\big(2 a x_1 + b \big)^2+1}} - \dfrac{2 a x_0 + b}{\sqrt{\big(2 a x_0 + b \big)^2+1}} \right) 
%   }{
%     (x_1 - x_0)
%   }
% \end{equation}

% \subsection{Theory}

@@

@@

\section{References}
\printbibliography[heading=none]

>>>>

\documentclass{article}
\usepackage{lmodern} % Latin Modern Font
\usepackage[T1]{fontenc}
\usepackage{amsfonts} % \mathbb
\usepackage[margin=0.5in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage[backend=biber, style=apa]{biblatex}
\usepackage{amsmath}
\usepackage{amssymb} % blackbox symbol
\usepackage{hyperref}
\usepackage{hypcap}
\DeclareMathOperator{\sign}{sign}
\bibliography{bibli}
\hypersetup{
  colorlinks=true, 
  allcolors=black,
  pdfauthor={Carlos Tarjano},
  pdftitle={Robust Digital Envelope Estimation Via Geometric Properties of an Arbitrary Real Signal}
}
\title{Robust Digital Envelope Estimation Via Geometric Properties of an Arbitrary Real Signal}
\author{Carlos Tarjano \and Valdecy Pereira}

@@

The angle $ \theta $ between the average direction and each of the vectors can be obtained via the relation of the slope of the respective lines, as in the expression $ \theta = \arctan( (m - \overline{m}) / (1 + m \overline{m}) ) $. The radii of the equivalent circles are thus given by $ r_l = x_l / \sin (\theta_l) $ with the curvature given by $\kappa_l =1/r_l=\sin (\theta_l) / x_l$.

\begin{equation} \label{eq:1}
  r_l = \left\lvert \frac{x_l \sqrt{\overline{m}^2 + 1} \ \sqrt{x_l^2 + y^2}}{\overline{m} x_l - y} \right\rvert
\end{equation}

@@

@@

While a theoretical basis for the normalization of the amplitude is given, and is justified in practice by the computational stability issues that might arise with arbitrary values, the algorithm is, from a pure mathematical point of view, impervious to amplitude scaling, as we now prove.

let $ s $ be a positive real number that multiplies every sample of a discrete wave $ W $. The subdivision in pulses of such a wave is unchanged by the vertical scaling operation, and we can write the slope of a line segment from a pulse to the next pulse with the same sign as $ m_l = (s y_{l + 1} - s y_l) / (x_{l + 1} - x_l) $.

Assuming, for the sake of simplicity, $ \overline{m} = 0 $, the radius of the equivalent circle of such a segment, as per equation \ref{eq:1}, is

$$ r_l =\left\lvert \frac{\sqrt{\left(s {y}_{l + 1} - s {y}_{l}\right)^{2} + \left({x}_{l + 1} - {x}_{l}\right)^{2}} \left({x}_{l + 1} - {x}_{l}\right)}{s {y}_{l + 1} - s {y}_{l}} \right\rvert $$

And the square of the distance $ d_l $ from the center of a circle $ C $ with that radius passing through the points defined by the coordinates of both pulses to the median point $\overline{p} = \big((x_l + x_{l + 1}) / 2, (y_l + y_{l + 1}) / 2\big) $ of the line segment is

$$ d_l^2 = - \frac{\left(s {y}_{l + 1} - s {y}_{l} - 2 {x}_{l + 1} + 2 {x}_{l}\right) \left(s {y}_{l + 1} - s {y}_{l} + 2 {x}_{l + 1} - 2 {x}_{l}\right) \left(s^{2} {y}_{l + 1}^{2} - 2 s^{2} {y}_{l + 1} {y}_{l} + s^{2} {y}_{l}^{2} + {x}_{l + 1}^{2} - 2 {x}_{l + 1} {x}_{l} + {x}_{l}^{2}\right)}{4 s^{2} \left({y}_{l + 1} - {y}_{l}\right)^{2}} $$

Assuming invariance to vertical scaling, $ \overline{p} $ lying inside or outside the circle must not depend on $ s $; $ |d_l| \le |r_l| \iff d_l^2 / r_l^2 \le 1 \iff \overline{p} \in C $.

$$ \frac{d_l^2}{r_l^2} = \frac{- \frac{s^{2} \left({y}_{i + 1}^{2} + {y}_{i}^{2}\right)}{4} + \frac{s^{2} {y}_{i + 1} {y}_{i}}{2} + ({x}_{i + 1} - {x}_{i})^{2}}{({x}_{i + 1} - {x}_{i})^{2}} \le 1$$

Reorganizing:

$$ y_{i + 1} y_i \le \frac{y_{i + 1}^2 + y_i^2}{2} \iff \overline{p} \in C $$

Thus, the circle $ C $ containing the point $\overline{p}$ doesn't depend on $ s $ nor on the horizontal parametrization of $ W \ quad \blacksquare $

\begin{figure}[ht!]
  \centering
    \includegraphics[width=0.8\linewidth]{10xRobustness.pdf}
  \caption{Minimum and maximum scales of the abscissa before computational stability issues arose, for a recording of a drumkit tom.}
  \label{fig:xRobustness}
\end{figure}

\begin{figure}[ht!]
  \centering
    \includegraphics[width=0.8\linewidth]{09yRobustness.pdf}
  \caption{Minimum and maximum values of the amplitude before computational stability issues arose, for a recording of a drumkit tom.}
  \label{fig:yRobustness}
\end{figure}

Figures \ref{fig:xRobustness} and \ref{fig:yRobustness} illustrate the computational resilience of the algorithm for scaling in both the abscissa and ordinate axes, respectively. Although mathematically independent of such parametrizations, in practice care must be taken, for different reasons, in the choice of values for both axes.
% TODO lack of standard and great number of samples

@@

\section{References}

\printbibliography[heading=none]
